---
title: "The Office Time Series"
author: "Larry D"
date: "3/19/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)

office_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-17/office_ratings.csv')

office_ratings$season_yr <- format(office_ratings$air_date, "%Y")
office_ratings$season_mo <- format(office_ratings$air_date, "%m")

```

## Total Votes by Season


```{r votes}
ggplot(office_ratings, aes(x=episode, y=total_votes,  fill=imdb_rating )) +
  geom_bar(stat = "identity") +
  facet_wrap(~paste("season",season))

```

## Total Votes to Ratings scatter plot

So from the time series plot it looks that votes is correlated
to imdb ratings.  Let's find out more with a scatter plot.

Note the season finale is highlighted by a larger point.

```{r ratings}
episodefinale <- tapply(office_ratings$episode, list(season=office_ratings$season), max)
office_ratings$finale <- ifelse(office_ratings$episode==rep(episodefinale, episodefinale),1,0)
datafinale <- office_ratings[which(office_ratings$finale==1),]

ggplot(office_ratings, aes(x=log(total_votes), y=imdb_rating)) +
  geom_point(aes(color=factor(season))) +
  geom_smooth(method="lm") +
  geom_point(data=datafinale, aes(x=log(total_votes), y=imdb_rating, color=factor(season)), size=4 )

```

So it seems that it is correlated to some degree.  The season finales
seemed to rate well.  Yet also notice that vote totals decrease as
the seasons progressed.  I suppose that is one reason why the show
ended after 9 season.

